Supercomputer parallel computations in solving the applied optimization problems

### 2017-10-07 2017/ParOptBook/Chapter6.tex
Chapter -> paper

\abstract*{The chapter considers dimensionality reduction scheme based on Peano-type space-filling cures (evolvents). The initial multidimensional optimization problem is substituted by an equivalent one-dimensional one based on the application of the mapping of a multidimensional search domain onto a segment of the real axis. A general description of the approach and its substantiations are given. The development of the classical scheme based on the application of a set of mappings and the implementation of new types of evolvents is considered for the parallel algorithm.}

\abstract{The chapter considers dimensionality reduction scheme based on Peano-type space-filling cures (evolvents). The initial multidimensional optimization problem is substituted by an equivalent one-dimensional one based on the application of the mapping of a multidimensional search domain onto a segment of the real axis. A general description of the approach and its substantiations are given. The development of the classical scheme based on the application of a set of mappings and the implementation of new types of evolvents is considered for the parallel algorithm.}

>>>>

\abstract*{The paper considers dimensionality reduction scheme based on Peano-type space-filling cures (evolvents). The initial multidimensional optimization problem is substituted by an equivalent one-dimensional one based on the application of the mapping of a multidimensional search domain onto a segment of the real axis. A general description of the approach and its substantiations are given. The development of the classical scheme based on the application of a set of mappings and the implementation of new types of evolvents is considered for the parallel algorithm.}

\abstract{The paper considers dimensionality reduction scheme based on Peano-type space-filling cures (evolvents). The initial multidimensional optimization problem is substituted by an equivalent one-dimensional one based on the application of the mapping of a multidimensional search domain onto a segment of the real axis. A general description of the approach and its substantiations are given. The development of the classical scheme based on the application of a set of mappings and the implementation of new types of evolvents is considered for the parallel algorithm.}

### 2017-10-07 2017/ParOptBook/Chapter8.tex
Chapter -> paper

\abstract*{In this chapter, the examples of solving the applied problems in the fields of optimal design (the finding of the optimum profile of a vehicle wheel), chemical research (finding the unknown kinetic parameters in the mathematical models of the complex chemical reactions), economics (the identification of the parameters in the regional economic model) are given.}

\abstract{In this chapter, the examples of solving the applied problems in the fields of optimal design (the finding of the optimum profile of a vehicle wheel), chemical research (finding the unknown kinetic parameters in the mathematical models of the complex chemical reactions), economics (the identification of the parameters in the regional economic model) are given.}

%\abstract{Each chapter should be preceded by an abstract (10--15 lines long) that summarizes the content. The abstract will appear \textit{online} at \url{www.SpringerLink.com} and be available with unrestricted access. This allows unregistered users to read the abstract as a teaser for the complete chapter. As a general rule the abstracts will not appear in the printed version of your book unless it is the style of your particular book or that of the series to which your book belongs.\newline\indent Please use the 'starred' version of the new Springer \texttt{abstract} command for typesetting the text of the online abstracts (cf. source file of this chapter template \texttt{abstract}) and include them with the source files of your manuscript. Use the plain \texttt{abstract} command if the abstract is also to appear in the printed version of the book.}

@@

Traditionally, the methods based on the random search ideas had been applied in IPC RAS for solving problem (\ref{8_chem_func}). The typical computation costs were several days of continuous computations. Within the framework of the joint research project by IPC RAS and Lobachevsky State University of Nizhni Novgorod it was proposed to apply the efficient parallel global optimization methods described in Chapter 5. %Ссылка на главу!!!!

@@

\section*{A brief conclusion}

In this chapter, some applied global optimization problems have been considered. All of these problems related with a search for optimal parameters for nonlinear relationships, which describe phenomenon or process under consideration. The first example is the finding of the optimum profile of a vehicle wheel. Solution to this problem allows to increase the maximum possible speed of the vehicle. The second one is related with chemical research (finding the unknown kinetic parameters in the mathematical models of the complex chemical reactions). The last example belongs to the field of economics. The problem of identification of the parameters for the regional economic model has been solved. Optimal parameters found with the global search algorithm allow to carry out scenario forecast calculations for the regional economy.

>>>>

\abstract*{In this paper, the examples of solving the applied problems in the fields of optimal design (the finding of the optimum profile of a vehicle wheel), chemical research (finding the unknown kinetic parameters in the mathematical models of the complex chemical reactions), economics (the identification of the parameters in the regional economic model) are given.}

\abstract{In this paper, the examples of solving the applied problems in the fields of optimal design (the finding of the optimum profile of a vehicle wheel), chemical research (finding the unknown kinetic parameters in the mathematical models of the complex chemical reactions), economics (the identification of the parameters in the regional economic model) are given.}

@@

Traditionally, the methods based on the random search ideas had been applied in IPC RAS for solving problem (\ref{8_chem_func}). The typical computation costs were several days of continuous computations. Within the framework of the joint research project by IPC RAS and Lobachevsky State University of Nizhni Novgorod it was proposed to apply the efficient parallel global optimization methods developed in UNN.

@@
